Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-15 paper/sec-results.tex
more edits

\section{Results of the cut-based analysis}

@@

In this section we present the results of the 
cut-based analysis described in the previous section, and provide 
cut-flows for the different analysis steps.
%
We
compare our results with other recent studies,
and assess how the signal significance
is affected if only the $4b$ component of the
QCD multi-jet background is taken into account (leaving out the 
the $2b2j$ and $4j$ components).
%
First we present the results in an environment with no pile-up,
followed by the corresponding analysis including PU effects.

@@

We now compare the cross-sections for
signal and background events at various
stages of the analysis.
%
We consider all relevant backgrounds (see Sect.~\ref{mcgeneration}),
and discuss how results are modified in the case where only the $4b$
background is considered.

In Table~\ref{tab:cutflowdetails}
the different
steps of the cut-flow in the present analysis are summarised,
separated into the boosted, intermediate,
    and resolved topologies.
    %
    The different analysis steps proceed as follows:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|c|c|c|}
\hline
&  Boosted  &   Intermediate &  Resolved  \\
\hline
\hline
{\bf C0} &  \multicolumn{3}{c|}{Generator level} \\
\hline
{\bf C1a} & $N_{\rm jets}^{R10}\ge 2$ & $N_{\rm jets}^{R04}\ge 2$, $N_{\rm jets}^{R10}=1$  &
$N_{\rm jets}^{R04}\ge 4$ \\
\hline
{\bf  C1b} & \multicolumn{3}{c|}{+$p_T$ cuts} \\
{\bf C1c} & \multicolumn{3}{c|}{+rapidity cuts}\\
\hline
 {\bf C1d} & +$N_{\rm MDT}\ge 2$ & +$N_{\rm jets}^{R10}=1$ with MDT  &
 +Higgs reconstruction \\
 \hline
{\bf C1e} & \multicolumn{3}{c|}{ +$m_H$ window cut} \\
\hline
{\bf C2} & \multicolumn{3}{c|}{+$b$-tagging}    \\
\hline
  \end{tabular}
  \caption{\small Definition of the cuts imposed successively for the boosted, intermediate
    and resolved selections.
    %
      \label{tab:cutflowdetails}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \begin{itemize}
    \item {\bf C0}:  generator level cross-sections, with
      mild generation cuts in the case of the background processes, and no
      generation cuts
      for the signal events.
      %
    \item {\bf C1a}:  check that we have at least
      two large-$R$ jets (in the boosted case),
      one large-$R$ jet and at least 2 small-$R$ jets (in the intermediate
      case) and at least four small-$R$ jets (in the resolved case).
      %
      No acceptance requirements are imposed.
    \item {\bf C1b}: require that the above jets should
      satisfy the corresponding $p_T$ thresholds;
      $p_T \ge 200$ GeV for large-$R$ jets and
      $p_T \ge 50$ GeV for small-$R$ jets.
    \item {\bf C1c}: jets are required to satisfy their associated
      rapidity acceptance constraints.
    \item {\bf C1d}: the two leading large-$R$ jets must
      be mass-drop tagged in the boosted category.
      %
      In the intermediate category, the large-$R$ jet must also be mass-drop tagged.
      %
    \item {\bf C1e}: after the two Higgs candidates  have been reconstructed,
      their invariant masses are required to lie within a window around $m_H$,
      in particular between 85 and 165 GeV.
          \item {\bf C2}: the
            $b$-tagging conditions are
            imposed (see
            Sect.~\ref{sec:btagging}), and the event is categorised exclusively
            into one of the three topologies.
      \end{itemize}
    Signal and background events satisfying all the analysis cuts up to the
    C2 level
    are then used as input for the MVA training, to be described next
    in Sect.~\ref{sec:mva}.
    %
    In Table~\ref{tab:cutflow_noPU_1} we collect
    the values for signal and background cross-sections
    for different steps of the cut-flow.
    %
    Results are divided into the resolved, intermediate and boosted categories,
    and are inclusive up to the C2 level, where exclusivity is imposed.
    %

In Table~\ref{tab:cutflow_noPU_1} we also  provide the signal over
      background ratio, $S/B$, and the signal
      significance, $S/\sqrt{B}$, corresponding to an integrated
      luminosity of $\mathcal{L}=3$ ab$^{-1}$.
      %
      These are provided both taking into account all the background components and only
      the $4b$ QCD background.
        %
      We find that after $b$-tagging, the  $2b2j$ component is
      of the same order of magnitude as the $4b$ component.
      %
      This implies that the signal significance at the end of the cut-based
      analysis is degraded by about a factor of two due to the contribution
      of light and charm jets being mis-identified as $b$-jets.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \scriptsize
  \input{table_noPU_1.tex}
  $\,$ \\
  \vspace{0.5cm}
  \input{table_noPU_2.tex}
  $\,$ \\
  \vspace{0.5cm}
    \input{table_noPU_3.tex}
    \caption{\small The cross-sections, in femtobarns,
      for the signal and the various background
      processes at different steps of the
      cut-flow, for the resolved (upper table),
      intermediate (middle table) and boosted
      (lower table) categories, for the analysis
      without PU.
      %
      For each step, the signal over
      background ratio $S/B$, and the signal
      significance $S/\sqrt{B}$ are also provided, considering either
      the total background or just the $4b$ component. Signal
      significances are calculated for a total integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$.
      %
      The different steps of the cut-flow are summarized
      in Table~\ref{tab:cutflowdetails}.
 \label{tab:cutflow_noPU_1}}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
In the boosted category, at the end of the cut-based
analysis, we find that around $10^3$ events
are expected
at the HL-LHC, with however a very large number,
$\simeq 10^6$, of QCD background events.
%
This leads to a pre-MVA signal significance of
$S/\sqrt{B}=1.2$ and a signal over background
ratio of $S/B=1.4\%$.
%
From  Table~\ref{tab:cutflow_noPU_1}
it is also possible to compute the corresponding pre-MVA
expectations for the LHC Run II with
$\mathcal{L}=300$ fb$^{-1}$: one expects around
120 signal events, with signal significance dropping down to
$S/\sqrt{B}\sim 0.3$.
%
We emphasize that such signal
significances could have been enhanced
by applying tighter selection requirements,
but our analysis cuts have been left deliberately loose
in order that such optimsation may be performed by the MVA.
%
Both the intermediate and resolved categories benefit from higher signal yields,
specially in the resolved category, but this enhancement is compensated for by the
corresponding
increase in the QCD multi-jet background.
%
In both categories
the signal significance is similar to that of the boosted category,
$S\sqrt{B}\simeq 0.9$.
%
An important additional
drawback of the resolved case is
that $S/B$
is one order to magnitude smaller.
%
Combining the pre-MVA results
from the
of the boosted, intermediate and resolved categories,
we obtain an overall
significance for the observation of the Higgs pair production
in the $b\bar{b}b\bar{b}$ final
state at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$
of  $S/\sqrt{B} \simeq 1.8$.

@@

One of the main differences of the present study as compared
to previous works is in the inclusion of both irreducible
and reducible background components, which allows us to
quantify
the impact of light and charm jet mistags. 
%
Two recent studies that have also studied the
feasibility of SM Higgs pair production in the $b\bar{b}b\bar{b}$
final state are from the UCL group~\cite{Wardrope:2014kya} and from
the
Durham group~\cite{deLima:2014dta}.
%
The UCL study is based
on requiring at least four $b$-tagged $R=0.4$ anti-$k_T$ jets
in central acceptance with $p_T \ge 40$ GeV, which are
then used to construct dijets (Higgs candidates) with
$p_T \ge 150$ GeV, $85 \le m_{\rm dijet} \le 140$ GeV
and $\Delta R \le 1.5$ between the two components
of the dijet.
%
In addition to the basic selection cuts, the constraints
from additional kinematic variables are included by means of a 
Boosted Decision Tree (BDT) discriminant.
%
The backgrounds included are the $4b$ and
$2b2c$ QCD multijets, as well as
$t\bar{t}$, $Zh$, $t\bar{t}h$ and $hb\bar{b}$,
and a signal significance of $S/\sqrt{B}\simeq 2.1$ for the HL-LHC
is obtained.

@@

 From the results of Table~\ref{tab:cutflow_noPU_1}, we observe
 that the signal significance for the boosted, intermediate,
 and resolved categories is increased to 2.7, 1.6 and 1.6, respectively,
 when only the QCD $4b$ background is included.
 %
 Combining in this
 case the signal significance in the three categories,
 we
 obtain $S/\sqrt{B_{\rm 4b}}\simeq 3.5$, which is twice
 as large as the result found when
 all background components are included.
 %
 At this level, part of the improvement that we found as compared
 to~\cite{deLima:2014dta,Wardrope:2014kya} arises
 from the combination of the three exclusive event topologies,
 as opposed the exploitation of a single specific category.

 It is interesting to compare in each category the interplay
 between the reducible and irreducible components of the
 QCD backgrounds.
 %
 In all cases, the $4b$ and $2b2j$ have comparable
 magnitudes, taking into account the size that the higher-order QCD
 effects could induce in
 the corresponding normalizations.
 %
 On the other hand, the $4j$ component
is always smaller by at least
 one order of magnitude.
 %
  So while the $4j$ component can be safely
 neglected, the inclusion of the
 $2b2j$ component is essential to robustly assess the feasibility
 of measuring Higgs pairs in this final state,
 especially
 in the boosted category.
 %
 This has the important
 consequence that a promising avenue to improve the prospects
 of this measurement would be to reduce, as much as possible,
 the light and charm jet mis-identification rate.

 In Fig.~\ref{fig:histoBack} we show a
 comparison
    of the shapes of the $4b$ and $2b2j$
    components of the QCD background for the transverse momentum
    $p_T$ of the leading
Higgs candidate in the resolved
and boosted  categories, and the same
 for the invariant
mass $m_{hh}$ of the
    reconstructed di-Higgs system.
    %
    The two components possess a rather similar shape
    for the two distributions, albeit with some interesting
    differences For instance, in the boosted
    category the $4b$ component is harder for the
    $p_T^h$ distribution.
  %
    The $2b2j$ component has a longer
    tail at small values of the $m_{hh}$ invariant
    mass distribution.
%
    We also observe that the $2b2j$ distributions
    are affected by somewhat larger
    Monte Carlo fluctuations as compared to $4b$, despite the large size
of the initial sample.
%
These fluctuations illustrate the challenge
of an accurate modelling of the effects
of $b$-jet mis-identification in QCD processes, which requires
very large MC samples.

@@

% The reason why the  $2b2j$ process
% cannot be neglected as compared to the $4b$ component
% is the following.
%
In the boosted category 
the cross-section  before
$b$-tagging is more than two orders
of magnitude larger in the $2b2j$
sample as compared to the $4b$ sample.
%
After $b$-tagging, a naive assessment would
suggest a suppression of the $2b2j$ cross-section by a factor $(f_l/f_b)^2 \simeq
1.5\cdot 10^{-4}$, as compared to the $4b$ component,
since a total of four $b$-tags are required to classify the
event as a Higgs candidate.
%
In which case the ratio of $2b2j$ over $4b$ would be
around $\simeq 3\%$, and therefore negligible.
  %
While  we have checked that this expectation is borne
out at the parton level,
we find that  when parton shower effects
are accounted for the situation is different, due both to radiation of $b\bar{b}$ pairs
and from selection effects.
%
Due to these effects,
the
number of  $b$ quarks in the  final state is
increased substantially in the $2b2j$ component as compared
to the parton level, while at the same
time the number of events in the $4b$ sample
with 4 $b$-jets is reduced.

We can make these statements more quantitative in the following way.
%
To first approximation, and neglecting the contribution from
charm mis-identification,
the
overall efficiency of the $b$-tagging requirements in the resolved category will be
given by the following expression:
\be
\label{btaggingeff}
{\rm EFF}_{\rm b-tag}\simeq \sum_{j=0}^{4}n^{\rm (b-jet)}_j\cdot f_b^{j}\cdot f_l^{4-j} \, ,
\ee
with $n^{\rm (b-jet)}_j$ being the fraction of events satisfying all the selection cuts,
where $j$ jets out of the leading four jets of the event
contain $b$ quarks (with $p_T^b\ge 15$
GeV).
%
Similar expressions can be derived for
the boosted and intermediate categories.
%
The naive expectation is that all events in the $4b$ sample have $n^{\rm (b-jet)}_4\simeq 1$
and $n^{\rm (b-jet)}_j\simeq 0$ for $j\ne 4$, while the events in the $2b2j$ sample
should have $n^{\rm (b-jet)}_2\simeq 1$ and zero otherwise.
%
This leads to a ratio of overall $b$-tagging selection efficiencies
\be
\label{eq:naive}
\frac{ {\rm EFF}_{\rm b-tag} \lc 2b2j \rc}{{\rm EFF}_{\rm b-tag} \lc 4b\rc}
  \simeq
 \lp \frac{f_l}{f_b}\rp^2 \simeq 1.5\cdot 10^{-4} \, .
\ee
However, after the parton shower the above approach is no longer accurate.
%
First of all, we will have a non-negligible fraction $n^{\rm (b-jet)}_j$
with $j=3,4$ also in the $2b2j$ sample, due to $b$-quark pair radiation
during the shower.
%
Secondly, not all events in the $4b$ sample will lead to four small-$R$ $b$-jets,
due to a combination of selection cuts and
parton shower effects.
%

@@

In Table~\ref{tab:btaggingcheck} we collect
the values of $n^{\rm (b-jet)}_j$ for the signal and the three QCD background samples.
%
We find that rather than the estimate Eq.~(\ref{eq:naive}),
the correct ratio of $b$-tagging selection efficiencies is instead
\be
\frac{{\rm EFF}_{\rm b-tag} \lc 2b2j\rc}{{\rm EFF}_{\rm b-tag} \lc 4b\rc}=
  \frac{0.04\%}{8.4\%} \simeq 5\cdot 10^{-3} \, .
  \ee
  This suppression factor is of the same order of the ratio of $4b$ to $2b2j$ cross-sections
  in the resolved category before $b$-tagging, shown
  in Table~\ref{tab:cutflow_noPU_1}.
    %
    This explains why the $2b2j$ contribution cannot be neglected as compared
    to the irreducible $4b$ component of the QCD background.
    %
    A similar calculation from the numbers in Table~\ref{tab:btaggingcheck} shows
    that, on the other hand, the $4j$ component of the background can typically
    be safely neglected.

>>>>

\clearpage
\section{Results of the cut-based analysis}

@@

In this section we present the results of the 
cut-based analysis described in the previous section, and provide 
cut-flows for the different analysis steps.
%
We
compare our results with other recent studies,
and assess how the signal significance
is affected if only the $4b$ component of the
QCD multi-jet background is taken into account.
%
Here we present the results in an environment without pile-up,
followed in the next section by the corresponding analysis including PU.

@@

Here we compare the cross-sections for
signal and background events at various
stages of the analysis.
%
We consider all relevant backgrounds (see Sect.~\ref{mcgeneration}),
and discuss how results are modified in the case where only the $4b$
background is considered.
%
In Table~\ref{tab:cutflowdetails}
the different
steps of the cut-flow in the present analysis are summarised,
separated into the boosted, intermediate,
    and resolved topologies.
    %
    The different analysis steps proceed as follows:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|c|c|c|}
\hline
&  Boosted  &   Intermediate &  Resolved  \\
\hline
\hline
{\bf C0} &  \multicolumn{3}{c|}{Generator level} \\
\hline
{\bf C1a} & $N_{\rm jets}^{R10}\ge 2$ & $N_{\rm jets}^{R04}\ge 2$, $N_{\rm jets}^{R10}=1$  &
$N_{\rm jets}^{R04}\ge 4$ \\
\hline
{\bf  C1b} & \multicolumn{3}{c|}{+$p_T$ cuts and rapidity cuts} \\
\hline
 {\bf C1c} & +$N_{\rm MDT}\ge 2$ & +$N_{\rm jets}^{R10}=1$ with MDT  &
 +Higgs reconstruction \\
 \hline
{\bf C1d} & \multicolumn{3}{c|}{ +$m_H$ window cut} \\
\hline
{\bf C2} & \multicolumn{3}{c|}{+$b$-tagging}    \\
\hline
  \end{tabular}
  \caption{\small Definition of the cuts imposed successively for the boosted, intermediate
    and resolved selections.
    %
      \label{tab:cutflowdetails}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \begin{itemize}
    \item {\bf C0}:  generator level cross-sections, with
      mild generation cuts in the case of the background processes, and no
      generation cuts
      for the signal events.
      %
    \item {\bf C1a}:  check that we have at least
      two large-$R$ jets (in the boosted case),
      one large-$R$ jet and at least 2 small-$R$ jets (in the intermediate
      case) and at least four small-$R$ jets (in the resolved case).
      %
      No acceptance requirements are imposed.
    \item {\bf C1b}: require that the above jets should
      satisfy the corresponding $p_T$ thresholds;
      $p_T \ge 200$ GeV for large-$R$ jets and
      $p_T \ge 50$ GeV for small-$R$ jets, and well as
      satisfy the associated
      rapidity acceptance constraints.
    \item {\bf C1c}: the two leading large-$R$ jets must
      be mass-drop tagged in the boosted category.
      %
      In the intermediate category, the large-$R$ jet must also be mass-drop tagged.
      %
    \item {\bf C1d}: after the two Higgs candidates  have been reconstructed,
      their invariant masses are required to lie within a window around $m_H$,
      in particular between 85 and 165 GeV.
          \item {\bf C2}: the
            $b$-tagging conditions are
            imposed (see
            Sect.~\ref{sec:btagging}), and the event is categorised exclusively
            into one of the three topologies.
      \end{itemize}
    Signal and background events satisfying all the analysis cuts up to the
    C2 level
    are then used as input for the MVA training, to be described next
    in Sect.~\ref{sec:mva}.

    In Table~\ref{tab:cutflow_noPU_1} we collect
    the values for signal and background cross-sections
    for different steps of the cut-flow.
    %
    Results are divided into the resolved, intermediate and boosted categories,
    and are inclusive up to the C2 level, where exclusivity is imposed.
    %
In Table~\ref{tab:cutflow_noPU_1} we also  provide the signal over
      background ratio, $S/B$, and the signal
      significance, $S/\sqrt{B}$, corresponding to an integrated
      luminosity of $\mathcal{L}=3$ ab$^{-1}$.
      %
      These are provided both taking into account all the background components and only
      the $4b$ QCD background.
        %
      We find that after $b$-tagging, the  $2b2j$ component is
      of the same order of magnitude as the $4b$ component in all categories.
      %
      This implies that the signal significance at the end of the cut-based
      analysis is degraded due to the contribution
      of light and charm jets being mis-identified as $b$-jets.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \scriptsize
  \input{table_noPU_1.tex}
  $\,$ \\
  \vspace{0.5cm}
  \input{table_noPU_2.tex}
  $\,$ \\
  \vspace{0.5cm}
    \input{table_noPU_3.tex}
    \caption{\small The cross-sections (fb)
      for the signal and the background
      processes at different steps of the
      cut-flow, for the resolved (upper table),
      intermediate (middle table) and boosted
      (lower table) categories, for the analysis
      without PU.
      %
      For each step, the signal over
      background ratio $S/B$, and the signal
      significance $S/\sqrt{B}$ are also provided, considering either
      the total background or just the $4b$ component. Signal
      significances are calculated for an
      integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$.
      %
      The different steps of the cut-flow are described
      in Table~\ref{tab:cutflowdetails}.
 \label{tab:cutflow_noPU_1}}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
In the boosted category, at the end of the cut-based
analysis, we find that around $10^3$ events
are expected
at the HL-LHC, with however a very large number,
$\simeq 10^6$, of QCD background events.
%
This leads to a pre-MVA signal significance of
$S/\sqrt{B}=1.2$ and a signal over background
ratio of $S/B=0.14\%$.
%
From Table~\ref{tab:cutflow_noPU_1}
it is also possible to compute the corresponding pre-MVA
expectations for the LHC Run II with
$\mathcal{L}=300$ fb$^{-1}$: one expects around
120 signal events, with signal significance dropping down to
$S/\sqrt{B}\sim 0.3$.
%
Such signal
significances could have been enhanced
by applying tighter selection requirements,
but our analysis cuts have been left deliberately loose
in order that such optimsation may be performed by the MVA.

The resolved category benefits from higher signal yields,
but this enhancement is compensated for by the
corresponding
increase in the QCD multi-jet background.
%
In both resolved and intermediate categories
the signal significance is similar to that of the boosted category,
$S\sqrt{B}\simeq 0.9$.
%
An further
drawback of the resolved case is
that $S/B$
is one order to magnitude smaller than in the boosted case.
%
Combining the pre-MVA results
from the boosted, intermediate and resolved categories,
we obtain an overall
significance for the observation of the Higgs pair production
in the $b\bar{b}b\bar{b}$ final
state at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$
of  $S/\sqrt{B} \simeq 1.8$.

@@

One of the main differences of the present study as compared
to previous works is in the inclusion of both irreducible
and reducible background components, which allows us to
quantify
the impact of light and charm jet mis-identification. 
%
Two recent studies that have also studied the
feasibility of SM Higgs pair production in the $b\bar{b}b\bar{b}$
final state are from the UCL group~\cite{Wardrope:2014kya} and from
the
Durham group~\cite{deLima:2014dta}.
%
The UCL study is based
on requiring at least four $b$-tagged $R=0.4$ anti-$k_T$ jets
in central acceptance with $p_T \ge 40$ GeV, which are
then used to construct dijets (Higgs candidates) with
$p_T \ge 150$ GeV, $85 \le m_{\rm dijet} \le 140$ GeV
and $\Delta R \le 1.5$ between the two components
of the dijet.
%
In addition to the basic selection cuts, the constraints
from additional kinematic variables are included by means of a 
Boosted Decision Tree (BDT) discriminant.
%
The backgrounds included are the $4b$ and
$2b2c$ QCD multijets, as well as
$t\bar{t}$, $Zh$, $t\bar{t}h$ and $hb\bar{b}$,
and a signal significance of $S/\sqrt{B}\simeq 2.1$ for the HL-LHC
is obtained.

@@

 From our results in Table~\ref{tab:cutflow_noPU_1}, we observe
 that the signal significance for the boosted, intermediate,
 and resolved categories is increased to 2.7, 1.6 and 1.6, respectively,
 when only the QCD $4b$ background is included.
 %
 Combining in this
 case the signal significance in the three categories,
 we
 obtain $S/\sqrt{B_{\rm 4b}}\simeq 3.5$, which is twice
 as large as the result found when
 all background components are included.
 %
 Part of the improvement 
with respect to~\cite{deLima:2014dta,Wardrope:2014kya} arises
 from the combination of the three exclusive event topologies,
 as opposed the exploitation of a single specific category.

 Also from Table~\ref{tab:cutflow_noPU_1}, we
 can compare the interplay
 between the reducible and irreducible components of the
 QCD backgrounds.
 %
 In all cases, the $4b$ and $2b2j$ have comparable
 magnitudes within the uncertainties from missing higher-order
 corrections.
 %
 On the other hand, the $4j$ component
is always smaller by at least
 one order of magnitude.
 %
  So while the $4j$ component can be safely
 neglected, the inclusion of the
 $2b2j$ component is essential to robustly assess the feasibility
 of measuring Higgs pairs in this final state,
 especially
 in the boosted category.
 %
 This has the important
 consequence that a promising avenue to improve the prospects
 of this measurement would be to reduce, as much as possible,
 the light and charm jet mis-identification rate.

 In Fig.~\ref{fig:histoBack} we show a
 comparison
    of the shapes of the $4b$ and $2b2j$
    components of the QCD background for the transverse momentum
    $p_T$ of the leading
Higgs candidate in the resolved
and boosted  categories, and the same
 for the invariant
mass $m_{hh}$ of the
    reconstructed di-Higgs system.
    %
    The two components possess a rather similar shape
    for the two distributions, albeit with some 
    differences.
  %
    For instance, in the boosted
    category the $4b$ component is harder for the
    $p_T^h$ distribution.
  %
    The $2b2j$ component has a longer
    tail at small values of the $m_{hh}$ invariant
    mass distribution.
%
    We also observe that the $2b2j$ distributions
    are affected by somewhat larger
    Monte Carlo fluctuations as compared to $4b$, despite the large size
of the initial sample.
%

@@

In the resolved category 
the cross-section  before
$b$-tagging is more than two orders
of magnitude larger in the $2b2j$
sample as compared to the $4b$ sample.
%
After $b$-tagging, a naive assessment would
suggest a suppression of the $2b2j$ cross-section by a factor $(f_l/f_b)^2 \simeq
1.5\cdot 10^{-4}$, as compared to the $4b$ component,
since a total of four $b$-tags are required to classify the
event as a Higgs candidate.
%
In which case the ratio of $2b2j$ over $4b$ would be
around $\simeq 3\%$, and therefore negligible.
  %
While  we have checked that this expectation is borne
out at the parton level,
we find that  when parton shower effects
are accounted for the situation is different, due both to radiation of $b\bar{b}$ pairs
and from selection effects.
%
Due to these effects,
the
number of  $b$ quarks in the  final state is
increased substantially in the $2b2j$ component as compared
to the parton level, while at the same
time the number of events in the $4b$ sample
with 4 $b$-jets is reduced.

We can make these statements more quantitative in the following way.
%
To first approximation, and neglecting the contribution from
charm mis-identification,
the
overall efficiency of the $b$-tagging requirements in the resolved category will be
given by the following expression:
\be
\label{btaggingeff}
{\rm EFF}_{\rm b-tag}\simeq \sum_{j=0}^{4}n^{\rm (b-jet)}_j\cdot f_b^{j}\cdot f_l^{4-j} \, ,
\ee
with $n^{\rm (b-jet)}_j$ being the fraction of events satisfying all the selection
requirements,
where $j$ jets out of the leading four jets of the event
contain $b$ quarks (with $p_T^b\ge 15$
GeV).
%
Similar expressions can be derived for
the boosted and intermediate categories.
%
The naive expectation is that all events in the $4b$ sample have $n^{\rm (b-jet)}_4\simeq 1$
and $n^{\rm (b-jet)}_j\simeq 0$ for $j\ne 4$, while the events in the $2b2j$ sample
should have $n^{\rm (b-jet)}_2\simeq 1$ and zero otherwise.
%
This leads to a ratio of overall $b$-tagging selection efficiencies
\be
\label{eq:naive}
\frac{ {\rm EFF}_{\rm b-tag} \lc 2b2j \rc}{{\rm EFF}_{\rm b-tag} \lc 4b\rc}
  \simeq
 \lp \frac{f_l}{f_b}\rp^2 \simeq 1.5\cdot 10^{-4} \, .
\ee
However, after the parton shower the above approach is no longer accurate.
%
First of all, we will have a non-negligible fraction $n^{\rm (b-jet)}_j$
with $j=3,4$ also in the $2b2j$ sample, due to $b$-quark pair radiation
during the shower.
%
Secondly, not all events in the $4b$ sample will lead to four small-$R$ $b$-jets,
due to a combination of selection cuts and
parton shower effects.
%

@@

In Table~\ref{tab:btaggingcheck} we collect
the values of $n^{\rm (b-jet)}_j$ for the signal and the three QCD background samples.
%
We find that rather than the estimate Eq.~(\ref{eq:naive}),
the correct ratio of $b$-tagging selection efficiencies is instead
\be
\frac{{\rm EFF}_{\rm b-tag} \lc 2b2j\rc}{{\rm EFF}_{\rm b-tag} \lc 4b\rc}=
  \frac{0.04\%}{8.4\%} \simeq 5\cdot 10^{-3} \, .
  \ee
  This suppression factor is of the same order of the ratio of $4b$ to $2b2j$ cross-sections
  in the resolved category before $b$-tagging, see Table~\ref{tab:cutflow_noPU_1}.
    %
    This explains why the $2b2j$ contribution cannot be neglected as compared
    to the irreducible $4b$ component of the QCD background.
    %
    A similar calculation from the numbers in Table~\ref{tab:btaggingcheck} shows
    that, on the other hand, the $4j$ component of the background can typically
    be safely neglected.
